### 2022-06-25 README.Rmd
update 2022-06-25 11:08:06

Before installing the package, please read [this vignette](https://cjvanlissa.github.io/worcs/articles/setup.html), which explains how to set up your computer for `worcs`.

After reading [the vignette](https://cjvanlissa.github.io/worcs/articles/setup.html), you can install the development version of the `worcs` package from GitHub with:

``` r
if(!requireNamespace("remotes"))install.packages("remotes")
remotes::install_github("cjvanlissa/worcs", dependencies = TRUE, update = "never")
tinytex::install_tinytex()
worcs::git_user("your_name", "your_email")
```

If you intend to write APA style manuscripts, you can additionally install the `papaja` package:

``` r
install.packages("papaja", dependencies = TRUE, update = "never")

```

>>>>

Before installing the package, please read [this vignette](https://cjvanlissa.github.io/worcs/articles/setup.html), which explains how to set up your computer for `worcs` (using the CRAN version).

If you know what you're doing and you wish to install the development version of the `worcs` package from GitHub instead, you can use:

``` r
if(!requireNamespace("remotes")) install.packages("remotes")
remotes::install_github("cjvanlissa/worcs", dependencies = TRUE, update = "never")
```
